`flippant` -- An `R` package for the automated analysis of dithionite scramblase

### 2015-09-21 inst/manuscript/manuscript.rmd
Fix a typo;

analysis_timing_iqr <- round(
  diff(
    unlist(
      summary(analysis_timing)[c("lq", "uq")],
      use.names = FALSE)),
  2)
```
With `flippant` we present an integrated solution for data analysis in the 
context of dithionite scramblase assays. Requiring only basic familiarity with 
`R` [@r_core_team_r:_2015] as an environment for statistical computing and
graphics, scientists can quickly analyse such data and arrive at 
publication-grade graphics that offer extensive facilities for individual 
optimization and adaptation [@wickham_ggplot2_2009]. On a system running `Linux`
and `R` version `r paste(R.version[c("major","minor")], collapse = ".")`, the
statements generating equivalents to the plots and calculations presented here
take a mere `r analysis_timing_median` seconds (IQR: `r analysis_timing__iqr` s;
$n==`r analysis_timing_n`$).

>>>>

analysis_timing_iqr <- round(
  diff(
    unlist(
      summary(analysis_timing)[c("lq", "uq")],
      use.names = FALSE)),
  2)
```
With `flippant` we present an integrated solution for data analysis in the 
context of dithionite scramblase assays. Requiring only basic familiarity with 
`R` [@r_core_team_r:_2015] as an environment for statistical computing and
graphics, scientists can quickly analyse such data and arrive at 
publication-grade graphics that offer extensive facilities for individual 
optimization and adaptation [@wickham_ggplot2_2009]. On a system running `Linux`
and `R` version `r paste(R.version[c("major","minor")], collapse = ".")`, the
statements generating equivalents to the plots and calculations presented here
take a mere `r analysis_timing_median` seconds (IQR: `r analysis_timing_iqr` s;
$n==`r analysis_timing_n`$).
